VM-Centric Snapshot Deduplication with Fault Isolation for Converged Cloud Architectures

### 2014-01-31 snapshot_system/paper_analysis.tex
updates

\noindent {\bf $r \le d<r_c$:}  In this case there is no PDS data loss and we need to look at the non-PDS data loss. 
The full snapshot availability of a VM is: 
%\begin{equation}
%\label{eq:VC1}
%(1-\frac{\binom{d}{r}} { \binom{p}{r} })^{N_1}.
\[
A(r)^{N_1}.
\]
%\end{equation}
Since $N_1$ is typically much smaller than $N_o$, 
the VC approach has a higher availability of VM snapshots than VO in this case.
%In the evaluation discussed in Section~\ref{sect:evaldedup}, 
%We have considered a worst case scenario where
%every PDS FSB is shared by all VMs in the VC approach, which leads a large $N_2$ value. 
%Even with $N_2$ being much higher than $N_o$ (as discussed below),
%the availability of VC snapshots is much higher than VO.

\noindent {\bf $r_c \leq d$:} Both non-PDS and PDS file system blocks in VC can have a loss.
The full snapshot availability of  a VM in the VC approach is
%\begin{equation}
%\label{eq:VC2}
% (1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
% *
% (1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
\[
A(r)^{N_1} * A(r_c)^{N_2}.
\]
That is still smaller than that of $V_O$ based on the observations of our data. There are two reasons for this:  
1) $N_1$ is much smaller than $N_o$ and we are observing that $N_1+N_2<N_o$. 
2)  $A(r) < A(r_c)$ because $r < r_c$.  
Table~\ref{tab:fsb-availability} lists the $A(r)$ values with
%that the availability of an individual file system block
different replication degrees, to demonstrate the gap between  $A(r)$ and  $A(r_c)$.
%\end{equation}
%comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
%In the evaluation discussed in Section~\ref{sect:evaldedup},
%We have considered a worst case scenario that
%every PDS FSB is shared by all VMs in the VC approach, which leads to a large $N_2$ value. 
%Even with that, the availability of VC snapshots is still much higher than VO and

>>>>

\noindent $r \le d<r_c$:  In this case there is no PDS data loss and we need to look at the non-PDS data loss. 
The full snapshot availability of a VM is: 
%\begin{equation}
%\label{eq:VC1}
%(1-\frac{\binom{d}{r}} { \binom{p}{r} })^{N_1}.
\[
A(r)^{N_1}.
\]
%\end{equation}
Since $N_1$ is typically much smaller than $N_o$, 
the VC approach has a higher availability of VM snapshots than VO in this case.
%In the evaluation discussed in Section~\ref{sect:evaldedup}, 
%We have considered a worst case scenario where
%every PDS FSB is shared by all VMs in the VC approach, which leads a large $N_2$ value. 
%Even with $N_2$ being much higher than $N_o$ (as discussed below),
%the availability of VC snapshots is much higher than VO.

\noindent $r_c \leq d$: Both non-PDS and PDS file system blocks in VC can have a loss.
The full snapshot availability of  a VM in the VC approach is
%\begin{equation}
%\label{eq:VC2}
% (1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
% *
% (1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
\[
A(r)^{N_1} * A(r_c)^{N_2}.
\]
That is still smaller than that of $V_O$ based on the observations of our data. There are two reasons for this:  
1) $N_1$ is much smaller than $N_o$ and we are observing that $N_1+N_2<N_o$. 
2)  $A(r) < A(r_c)$ because $r < r_c$.  
Table~\ref{tab:fsb-availability} lists the $A(r)$ values with
%that the availability of an individual file system block
different replication degrees, to demonstrate the gap between  $A(r)$ and  $A(r_c)$.
%\end{equation}
%comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
%In the evaluation discussed in Section~\ref{sect:evaldedup},
%We have considered a worst case scenario that
%every PDS FSB is shared by all VMs in the VC approach, which leads to a large $N_2$ value. 
%Even with that, the availability of VC snapshots is still much higher than VO and

### 2014-01-31 snapshot_system/paper_eval.tex
updates

We will compare VC with a VO approach  using stateless routing with binning (SRB) 
based on~\cite{Dong2011,extreme_binning09}.
SRB executes distributed deduplication by routing a data chunks to cluster machines~\cite{Dong2011}
using  a min-hash function discussed in \cite{extreme_binning09}. Once a data chunk is routed to
a machine, the chunk is compared with the fingerprint index within this machine locally.

>>>>

We will compare VC with a VO approach  using stateless routing with binning (SRB) 
based on~\cite{Dong2011,extreme_binning09}.
SRB executes distributed deduplication by routing data chunks to cluster machines~\cite{Dong2011}
using  a min-hash function discussed in \cite{extreme_binning09}. Once a data chunk is routed to
a machine, the chunk is compared with the fingerprint index within this machine locally.
